Contracts for unions and intersections are hard for Nickel

### 2021-06-04 paper.tex
Use port as user-defined contract example

Even more interesting, we could come up with a contract that checks that a function
maps \nickel{true} to \nickel{false} and \nickel{false} to \nickel{true}
by applying the function exhaustively and checking its results,
and then use it as a contract for the \nickel{not} function, as can be seen on Figure
\ref{fig:checked-not}.

\begin{figure}[h]
  \begin{center}
\begin{lstlisting}[language=nickel]
let NotC = contracts.fromPred (
  fun f => builtins.isFun f && (f true == false) && (f false == true)
) in
let checkedNot = not | #NotC
\end{lstlisting}
\end{center}
\caption{A contract that checks the not function behaves as expected}
\label{fig:checked-not}
\end{figure}

>>>>

Even more interesting, we could come up with a contract that checks that a function
maps \nickel{true} to \nickel{false} and \nickel{false} to \nickel{true}
by applying the function exhaustively and checking its results,
and then use it as a contract for the \nickel{not} function, as can be seen on Figure
\ref{fig:port-contract}.\unsure{These few paragraphs are out of date,
  even more so since Arnaud changed the flat contract example}

\begin{figure}[h]
  \begin{center}
\begin{lstlisting}[language=nickel]
let Port = contracts.fromPred (fun value =>
  builtins.isNum value && value % 1 == 0
  && value >= 0 && value <= 65353) in
80 | Port
\end{lstlisting}
\end{center}
\caption{A contract for valid ports}
\label{fig:port-contract}
\end{figure}
